### 2009-02-19 doc/ws-programming-tutorial/doc/tex_introduction/introduction.tex
Wrote more text for the time client

The HED which was already mentioned in the section above is an essential part of the ARC middleware. It provides hosting of various services at application level, as well as a number of modules~\cite{QIANG_2005}. Figure~\ref{fig:HED_internal} illustrates a typical setup of a server sided HED. The HED consists of a few compononents called Message Chain Components (MCC) which are ordered within a layered structure and several \textcolor{urgent}{modules} which shall aid the programmer to simplify the development of the Web Services (Config, Loader, Logging, XMLNode).
%
\begin{figure}
	\centering
	\includegraphics[width=10cm]{tex_introduction/HED.pdf}
	\mycaption{Example of HED structure with an Arex service and a file service.\task{ Replace image by an easier one!} }{\task{Write more stuff}}
\label{fig:HED_internal}
\end{figure}
The MCCs are passing the incoming and outgoing messages to the upper or the respective lower layer.
% AUFZÄHLUNG???
The lowest layer has to be a transport protocol like TCP which enables the transmission between the two applications, the client and the server. (The Internet Protocol (IP) beneath the TCP layer enables a transmission between two computers. IP is needed but not part of the HED.) TCP is well suited for the application because it provides a reliable and ordered delivery of a byte stream which is important to ensure security and a requirement for the usage of HTTP.
The TCP layer is followed by the Hypertext Transfer Protocol (HTTP). 
In case a security layer is desired, the TLS (Transport Layer Security formerly known as SSL, Secure Sockets Layer) can be inserted between the two layers TCP and HTTP.
The HTTP provides the client server architecture. It is stateless but offers several extensions for requests, header information and status codes. Furthermore HTTP enables the usage of Uniform Resource Locators (URL) which is used by KnowArc to multiplex between different services. The multiplexing layer needs to be defined within the HED and is called Plexer. Depending on the path of the URL the Plexer passes messages to a defined SOAP service which again passes the message to the Web Service.\\

>>>>

The HED which was already mentioned in the section above is an essential part of the ARC middleware. It provides hosting of various services at application level, as well as a number of modules~\cite{QIANG_2005}. Figure~\ref{fig:HED_internal} illustrates a typical setup of a server sided HED. The HED consists of a few compononents called Message Chain Components (MCC) which are ordered within a layered structure and several \textcolor{urgent}{modules} which shall aid the programmer to simplify the development of the Web Services (Config, Loader, Logging, XMLNode).
%
\begin{figure}
	\centering
	\includegraphics[width=14cm]{tex_introduction/HED.pdf}
	\mycaption{Example of HED structure with an Arex service and a file service.\task{ Replace image by an easier one!} }{\task{Write more stuff}\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - WEB SERVICE   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - WEB SERVICE}}
\label{fig:HED_internal}
\end{figure}
The MCCs are passing the incoming and outgoing messages to the upper or the respective lower layer.
% AUFZÄHLUNG???
The lowest layer has to be a transport protocol like TCP which enables the transmission between the two applications, the client and the server. (The Internet Protocol (IP) beneath the TCP layer enables a transmission between two computers. IP is needed but not part of the HED.) TCP is well suited for the application because it provides a reliable and ordered delivery of a byte stream which is important to ensure security and a requirement for the usage of HTTP.
The TCP layer is followed by the Hypertext Transfer Protocol (HTTP). 
In case a security layer is desired, the TLS (Transport Layer Security formerly known as SSL, Secure Sockets Layer) can be inserted between the two layers TCP and HTTP.
The HTTP provides the client server architecture. It is stateless but offers several extensions for requests, header information and status codes. Furthermore HTTP enables the usage of Uniform Resource Locators (URL) which is used by KnowArc to multiplex between different services. The multiplexing layer needs to be defined within the HED and is called Plexer. Depending on the path of the URL the Plexer passes messages to a defined SOAP service which again passes the message to the Web Service.\\

### 2009-02-19 doc/ws-programming-tutorial/doc/tex_timeservice/timeservice.tex
Wrote more text for the time client

\lstsetKSH
\begin{program}
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ arched -c arched_timeservice.xml && echo Daemon started || echo Daemon start failed
\end{lstlisting}
\end{program}

@@

\task{Hardcoded URL!!!}

\lstsetCPP
\lstinputlisting
	[
	label=lst:arcecho_time_client_cpp,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/timeclient/timeclient.cpp}

\lstsetKSH
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ ./timeclient
Wed Feb 18 11:20:30 2009
\end{lstlisting}
\end{minipage}

@@

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:arched_time_request,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:time="urn:time" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeRequest></timeRequest>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:arched_time_response,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeResponse>Wed Feb 18 11:20:30 2009</timeResponse>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

>>>>

To run the service again the arched command shown in~\ref{lst:arched_timeservice_ksh} has to be used.
\lstsetKSH
\begin{program}
\begin{lstlisting}[
label=lst:arched_timeservice_ksh,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ arched -c arched_timeservice.xml && echo Daemon started || echo Daemon start failed
Daemon started
\end{lstlisting}
\end{program}

@@

\task{\#ifdef HAVE\_CONFIG\_H\#include <config.h>\#endif - habe ich entfernt... macht keinen Sinn, da keine weiteren Macros im Source Code enthalten sind... oder?}
In the next step a simple client needs to be implemented whose task is to interprete the returned message of the client.
The client needs to have the same protocol stack as the daemon but in contrast to it, it does not need the ability to be loaded as a plugin. As one will see, the creation of this protocol stack on client side is very simple.
The source code of the client consists primarily of the main function and is to be seen in Listing~\ref{lst:time_client_cpp}.
In line~\ref{lst_code:time_client_cpp_logger} the logger is initialized and redirected to the standard error stream.
For the components of the protocol stack are likewise loaded dynamically, one need to specify the installation directory in line~\ref{lst_code:time_client_cpp_init} too.
\task{remark in \textbf{introduction}, what the plexer is for. In our case: to have several services running on one port!!!!!!!!}
The URL of the service is defined in line~\ref{lst_code:time_client_cpp_url}. It fits to the HED configuration file which was shown in Listing~\ref{lst:time_arched_xml}. The daemon is listing on port 60000 and is running on the localhost. The service itself uses HTTP and can be reached by using the path \textit{time}.
Line~\ref{lst_code:time_client_cpp_config} loads the standard config file which is usually almost empty. As a result, no additional security procedures will later be linked into the client sided stack. The protocol stack is created in line~\ref{lst_code:time_client_cpp_client}. Thanks to the URL the information for the configuration can be completed.
The constructor of the class \textit{ClientSOAP} creates a SOAP client which uses HTTP, addresses the port 60000 on localhost. If i.e. HTTPS would have been used, the stack would have been extended by a TLS layer.
Now the client stack is ready, one can create a request to the service. In line~\ref{lst_code:time_client_cpp_message_reqeust} a message which corresponds to the Listing~\ref{lst:time_client_request} is created. The message gets processed by the command in line~\ref{lst_code:time_client_cpp_message_response}. If everything was fine, the message will finally be send to the standard out in line~\ref{lst_code:time_client_cpp_message_answer}.

\lstsetCPP
\lstinputlisting
	[
	label=lst:time_client_cpp,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/timeclient/timeclient.cpp}

@@

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:time_client_request,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:time="urn:time" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeRequest></timeRequest>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:time_client_response,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeResponse>Wed Feb 18 11:20:30 2009</timeResponse>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

\lstsetKSH
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=st:time_client_ksh,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ ./timeclient
Wed Feb 18 11:20:30 2009
\end{lstlisting}
\end{minipage}
